Advances in Artificial Intelligence for Data Visualization: Developing Computer Vision Models to Automate Reading of Data Plots, with Application to Predictive Model Diagnostics

### 2022-03-10 Milestone_1/01-chap1.Rmd
fix reference

Similarly, @wilkinson_graph-theoretic_2005 proposed the work called graph theoretic scagnostics, which adopted the idea of "scagnostics" - scatter plot diagnostics from (can't find the 1984 citation). It includes 9 computable scagnostics measures defined on planar proximity graphs: "Outlying", "Convex", "Skinny", "Stringy", "Straight", "Monotonic", "Skewed", "Clumpy" and "Striated" which attempts to describe outliers, shape, density, trend and coherence of the data. This approach is inspiring but it still does not give the complete list of visual discoverable features. In fact, it is possible that such a list will never be complete as suggested in @buja_statistical_2009.

@@

Because the first project is still ongoing, we consider the result we have is not enough to write as a paper at the moment. Hence, the material provided in this section is two main parts of the draft paper that will contain enough details for understanding the project.

## Human Subject Exeriments

@@

On top of the pre-trained model, we added a 2D global average pooling layer [@lin_network_2014], followed by a fully-connected dense layer with 256 nodes, a dropout layer [@srivastava_dropout_nodate] with 20% dropout rate, and a output layer with softmax as activation function. A diagram of the model architecture is given in Figure \ref{fig:model-arch}.

>>>>

Similarly, @wilkinson_graph-theoretic_2005 proposed the work called graph theoretic scagnostics, which adopted the idea of "scagnostics" - scatter plot diagnostics from John and Paul Tukey. It includes 9 computable scagnostics measures defined on planar proximity graphs: "Outlying", "Convex", "Skinny", "Stringy", "Straight", "Monotonic", "Skewed", "Clumpy" and "Striated" which attempts to describe outliers, shape, density, trend and coherence of the data. This approach is inspiring but it still does not give the complete list of visual discoverable features. In fact, it is possible that such a list will never be complete as suggested in @buja_statistical_2009.

@@

Because the first project is still ongoing, we consider the result we have is not enough to write as a paper at the moment. Hence, the materials provided in this chapter are two main parts of the draft paper that will contain enough details for understanding the project.

## Human Subject Experiments

@@

On top of the pre-trained model, we added a 2D global average pooling layer [@lin_network_2014], followed by a fully-connected dense layer with 256 nodes, a dropout layer [@srivastava_dropout_2014] with 20% dropout rate, and a output layer with softmax as activation function. A diagram of the model architecture is given in Figure \ref{fig:model-arch}.

### 2022-03-10 Milestone_1/_book/thesis.tex
fix reference

Similarly, \textcite{wilkinson_graph-theoretic_2005} proposed the work called graph theoretic scagnostics, which adopted the idea of ``scagnostics'' - scatter plot diagnostics from (can't find the 1984 citation). It includes 9 computable scagnostics measures defined on planar proximity graphs: ``Outlying'', ``Convex'', ``Skinny'', ``Stringy'', ``Straight'', ``Monotonic'', ``Skewed'', ``Clumpy'' and ``Striated'' which attempts to describe outliers, shape, density, trend and coherence of the data. This approach is inspiring but it still does not give the complete list of visual discoverable features. In fact, it is possible that such a list will never be complete as suggested in \textcite{buja_statistical_2009}.

@@

Because the first project is still ongoing, we consider the result we have is not enough to write as a paper at the moment. Hence, the material provided in this section is two main parts of the draft paper that will contain enough details for understanding the project.

\hypertarget{human-subject-exeriments}{%
\section{Human Subject Exeriments}\label{human-subject-exeriments}}

@@

On top of the pre-trained model, we added a 2D global average pooling layer \autocite{lin_network_2014}, followed by a fully-connected dense layer with 256 nodes, a dropout layer \autocite{srivastava_dropout_nodate} with 20\% dropout rate, and a output layer with softmax as activation function. A diagram of the model architecture is given in Figure \ref{fig:model-arch}.

>>>>

Similarly, \textcite{wilkinson_graph-theoretic_2005} proposed the work called graph theoretic scagnostics, which adopted the idea of ``scagnostics'' - scatter plot diagnostics from John and Paul Tukey. It includes 9 computable scagnostics measures defined on planar proximity graphs: ``Outlying'', ``Convex'', ``Skinny'', ``Stringy'', ``Straight'', ``Monotonic'', ``Skewed'', ``Clumpy'' and ``Striated'' which attempts to describe outliers, shape, density, trend and coherence of the data. This approach is inspiring but it still does not give the complete list of visual discoverable features. In fact, it is possible that such a list will never be complete as suggested in \textcite{buja_statistical_2009}.

@@

Because the first project is still ongoing, we consider the result we have is not enough to write as a paper at the moment. Hence, the materials provided in this chapter are two main parts of the draft paper that will contain enough details for understanding the project.

\hypertarget{human-subject-experiments}{%
\section{Human Subject Experiments}\label{human-subject-experiments}}

@@

On top of the pre-trained model, we added a 2D global average pooling layer \autocite{lin_network_2014}, followed by a fully-connected dense layer with 256 nodes, a dropout layer \autocite{srivastava_dropout_2014} with 20\% dropout rate, and a output layer with softmax as activation function. A diagram of the model architecture is given in Figure \ref{fig:model-arch}.
